---
output:
    html_notebook:
        toc: true
        toc_float: true
editor_options:
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# `rdflib` - package review


#### This repo contains files associated with the **rOpenSci** review of **`rdflib`** (issue [\#169](https://github.com/ropensci/onboarding/issues/169)).

<br>

## package info

**Description:**

The Resource Description Framework, or 'RDF' is a widely used
             data representation model that forms the cornerstone of the 
             Semantic Web. 'RDF' represents data as a graph rather than 
             the familiar data table or rectangle of relational databases.
             The 'rdflib' package provides a friendly and concise user interface
             for performing common tasks on 'RDF' data, such as reading, writing
             and converting between the various serializations of 'RDF' data,
             including 'rdfxml', 'turtle', 'nquads', 'ntriples', 'trig', and 'json-ld';
             creating new 'RDF' graphs, and performing graph queries using 'SPARQL'.
             This package wraps the low level 'redland' R package which
             provides direct bindings to the 'redland' C library.  Additionally,
             the package supports the newer and more developer friendly
             'JSON-LD' format through the 'jsonld' package. The package
             interface takes inspiration from the Python 'rdflib' library.

**Author:** `r person("Carl", "Boettiger", 
                  email = "cboettig@gmail.com", 
                  role = c("aut", "cre", "cph"),
                  comment=c(ORCID = "0000-0002-1642-628X"))`

**repo url:** <https://github.com/cboettig/rdflib>

**website url:** <https://cboettig.github.io/rdflib/>

### Session info


```{r sessionInfo}
sessionInfo()
```

## Test installation

### test install of `rdflib` from GitHub with:

```{r test-github}
devtools::install_github("/")
```
```{r github-rm}
remove.packages("")
```

#### **comments:**

<!-- record comments on github install here -->

***

### test local `rdflib` install:

```{r test-local}
install.packages("/Users/Anna/Documents/workflows/packages/pkgreviewr/../rdflib")
```
#### **comments:**

<!-- record comments on local install here -->

***

### test `rdflib` for goodpractice:

```{r test-goodpractice}
goodpractice::goodpractice("rdflib")
```
#### **comments:**

<!-- record comments on goodpractice here -->

***

## check documentation

### test `rdflib` function help files:

```{r test-help}
help(package = "rdflib")
```

#### **comments:**

<!-- record comments on help files here -->

***

### test `rdflib` vignettes:

```{r test-vignettes}
vignette(package = "rdflib")
```

#### **comments:**

<!-- record comments on vignettes here -->

***

## `rdflib` play time!:

```{r free-style}
library("rdflib")
```
<!-- experiment with package function -->


<br>
<br>

#### **comments:**

<!-- record comments on rdflib experimentation here -->

***
