---
output: html_document
pagetitle: "Onboarding Report"
params:
  pkgdir: /Users/noamross/dropbox/reviews/plater
  save_obj: FALSE
---

```{r setup, include=FALSE}
library(knitr)
library(dplyr)
opts_chunk$set(echo = TRUE)
library(desc)
library(fs)
library(cloc)
library(spelling)
library(goodpractice)
library(covr)
library(purrr)
library(DT)
library(formattable)
```


```{r env, include = FALSE}
Sys.setlocale("LC_COLLATE", "C")
Sys.setenv("_R_CHECK_TIMINGS_"=0, "_R_CHECK_LENGTH_1_CONDITION_" = TRUE)
```

```{r get_description, include = FALSE}
pkgdesc <- desc(path(params$pkgdir, "DESCRIPTION"))
pkgname <- pkgdesc$get_field("Package")
```
# `r paste('Onboarding Submission Report: ', pkgname)` {.tabset}

## README

```{r readme, echo = FALSE, comment = ""}
if (file_exists(path(params$pkgdir, "README.md")))  {
  #knit_print(asis_output(paste(readLines(path(params$pkgdir, "README.md")), collapse = "\n")))
  readme_tmp <- tempfile()
  rmarkdown::pandoc_convert(path(params$pkgdir, "README.md"), to="html",
                               output = readme_tmp)
  knit_print(asis_output(
    paste(readLines(readme_tmp), collapse="\n")
  ))
} else if (length(dir_ls(params$pkgdir, regexp = "README", ignore.case = TRUE))) {
  cat(readLines(dir_ls(params$pkgdir, regexp = "README", ignore.case = TRUE)[1]), sep = "\n")
} else {
  knit_print(asis_output('<span style="color: red;"><strong>No README found!<strong/><span/>'))
}
```


## DESCRIPTION

```{r description, echo = FALSE, comment=""}
pkgdesc
```


## R CMD check

```{r get_gp, include = FALSE}
gp_obj <- safely(quietly(gp))(path = params$pkgdir)
```

```{r rcmdcheck, echo=FALSE, comment=""}
if(is.null(gp_obj$error)) {
cat(paste(
  gp_obj$result$result$rcmdcheck$stderr,
  "\n----------\n",
  gp_obj$result$result$rcmdcheck$stdout))
  gp_obj$result$result$rcmdcheck$session_info
}

```

## goodpractice

```{r rcmdcheck_warn, echo=FALSE, comment=""}
if(!is.null(gp_obj$error)) {
  stop(gp_obj$error)
}
if(!is.null(gp_obj$results$warnings)) {
  warning(gp_obj$result$warnings)
}
```

```{r gp, echo=FALSE, comment=""}
gp_obj$result$result
```

## Spelling

```{r spelling, echo = FALSE}
spell_obj <- spell_check_package(params$pkgdir)
spell_obj
```

## Tests

***TODO: Better way to explore test results?***

```{r tests, message = FALSE, warning=FALSE, echo = FALSE}
test_obj <- quietly(devtools::test)(params$pkgdir, reporter = testthat::SummaryReporter)
```

```{r tests2, message = FALSE, warning=FALSE, echo = FALSE}
fail_fmt <- formatter("span",
                      style = x ~ formattable::style("display" = "block", "padding" = "0 4px", "border-radius" = "4px",  "background-color" = ifelse(x, "lightpink", "white")))
skip_fmt <- formatter("span",
                      style = x ~ formattable::style("display" = "block", "padding" = "0 4px", "border-radius" = "4px",  "background-color" = ifelse(x, "yellow", "white")))

as.data.frame(test_obj$result) %>%
  mutate_at(vars(failed, skipped, error, warning), as.logical) %>%
  arrange(desc(failed), desc(error), desc(warning), desc(skipped)) %>% formattable(list(
  error = fail_fmt,
  skipped = skip_fmt,
  warning = fail_fmt,
  failed = fail_fmt
)) %>%
as.datatable(rownames=FALSE, autoHideNavigation = TRUE, width = "100%")
```

## Test Coverage

***TODO: Cleanup the widget for this and make in a function in the package***

```{r covr, echo=FALSE}
source("/home/rstudio/coverage-report-widget.R")
if(!is.null(gp_obj$result)) {
covr_report <- report_widget(gp_obj$result$result$covr$coverage)
covr_report
}
```

## Dependencies

***TODO: Show package dependency tree.  Best option is currently `r-lib/pkgdepenends`,
but current version broken, so using old commit.***

```{r pkgdepends, echo = FALSE, comment = "", error=TRUE}

pkgdepends_obj <- pkgdepends::remotes$new(paste0("installed::",
                                    system.file(package=pkgname)),
                            lib = tempfile())
pkgdepends_obj$solve()
pkgdepends_obj$draw_tree()
```

## CLOC

***TODO: Why are there no results when knitting here?***

```{r cloc, echo = FALSE}
cloc_obj <- cloc::cloc(params$pkgdir)

cloc_obj %>%
  mutate_at(vars(ends_with("pct")),
            funs(as.character(formattable::percent(., digits=1)))) %>%
  select(-source) %>% 
  DT::datatable(rownames = FALSE, width= "100%",  autoHideNavigation=TRUE)
```

## Functions / Help Topics

***TODOs***

-   Table of functions with
    -   name
    -   signature
    -   short help topic description
    -   cyclomatic complexity
    -   lines of code
    -   some measure of network importance (how many fns depend on it, how many package fns it calls (resursively))
-   Network of function dependencies
    -   use `igraph.from.graphNEL(makeCallGraph(as.list(getNamespace(pkgname))))`, **networkD3**?, **visNetwork**
    -   distinguish exported/internal functions
-   Some way to detect/show S3, S4, R6 usage?
-   Package PDF manual

```{r fns, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
if(!is.null(gp_obj$result)) {
  kable(gp_obj$result$result$cyclocomp, row.names = FALSE)
}
```


```{r, include = FALSE}
# Plan here is to render the manual and store it as a downloadable base64 object)
# mp <- tempdir()
# devtools::build_manual(pkg = params$pkgdir, path = mp)
# list.files(mp)
```

```{r, include = FALSE}
if(params$save_obj) {
  if(is.null(params$obj_dir)) {
    obj_dir <- file.path(params$pkgdir, "ro-check")
  } else {
    obj_dir <- params$obj_dir
  }
  if(!dir_exists(obj_dir)) dir_create(params$obj_dir)
  saveRDS(gp_obj, path(obj_dir, "gp_obj.rds"))
#  saveRDS(pkgdepends_obj, path(params$obj_dir, "pkgdepends.rds"))
  saveRDS(cloc_obj, path(obj_dir, "cloc_obj.rds"))
  saveRDS(spell_obj, path(obj_dir, "spell_obj.rds"))
  saveRDS(test_obj, path(obj_dir, "test_obj.rds"))
}
```


