---
title: "pkgreviewr for editors"
author: "Anna Krystalli"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pkgreviewr for editors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


`pkgreviewr` now also provides templates for editors. 

```{r, eval = F}
library(pkgreviewr)

pkgreview_create("nldoc/nlrx", 
                 review_parent = "~/Documents/workflows/rOpenSci/editorials/",
                 template = "editor")
```

As with initialising a review, the repo is downloaded into `review_parent`. 

It also creates a `pkgreviewr` project containing editor related templates: 

```
.
├── editor.md
├── index.Rmd
├── nlrx-review.Rproj
└── request.Rmd
```

### `index.Rmd`

Similar to a review project, `index.Rmd` is a pre-populated notebook where initial editor checks can be performed 


### `editor.md`

This file contains the editor checks response template

### `request.Rmd`

This contains a prepopulated parametarised `.Rmd` for generating request emails. The parameters it accepts are:

- person's name 
- some friendly banter
- whether JOSS submission is involved

Use:

```{r, eval=FALSE}
render_request()
```

to render the document by first launching a form in the browser to enter parameter values. Alternatively, you can manually edit the YAML header with parameter values and knit.

