---
output:
    html_notebook:
        toc: true
        toc_float: true
editor_options:
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(magrittr)
```

# `rdflib` - package review

## **Reviewer:** [\@annakrystalli](https://github.com/annakrystalli)

### Review Submitted:
**`r cat(sprintf("**Last updated:** %s", Sys.Date()))`**

***

<br>

This report contains documents the review of **rOpenSci** submitted package:

### **`rdflib`: ropensci/onboarding**  issue [\#169](https://github.com/ropensci/onboarding/issues/169).

<br>

## Package info

**Description:**

The Resource Description Framework, or 'RDF' is a widely used
             data representation model that forms the cornerstone of the 
             Semantic Web. 'RDF' represents data as a graph rather than 
             the familiar data table or rectangle of relational databases.
             The 'rdflib' package provides a friendly and concise user interface
             for performing common tasks on 'RDF' data, such as reading, writing
             and converting between the various serializations of 'RDF' data,
             including 'rdfxml', 'turtle', 'nquads', 'ntriples', and 'json-ld';
             creating new 'RDF' graphs, and performing graph queries using 'SPARQL'.
             This package wraps the low level 'redland' R package which
             provides direct bindings to the 'redland' C library.  Additionally,
             the package supports the newer and more developer friendly
             'JSON-LD' format through the 'jsonld' package. The package
             interface takes inspiration from the Python 'rdflib' library.

**Author:** `r person("Carl", "Boettiger", 
                  email = "cboettig@gmail.com", 
                  role = c("aut", "cre", "cph"),
                  comment=c(ORCID = "0000-0002-1642-628X"))`

**repo url:** <https://github.com/cboettig/rdflib>

**website url:** <https://cboettig.github.io/rdflib/>

## Review info


#### See [reviewer guidelines](https://github.com/ropensci/onboarding/blob/master/reviewing_guide.md) for further information on the rOpenSci review process.

**key review checks:**

- Does the code comply with **general principles in the [Mozilla reviewing guide](https://mozillascience.github.io/codeReview/review.html)**?
- Does the package **comply with the [ROpenSci packaging guide](https://github.com/ropensci/onboarding/blob/master/packaging_guide.md)**?
- Are there **improvements** that could be made to the **code style?**
- Is there **code duplication** in the package that should be reduced?
- Are there **user interface improvements** that could be made?
- Are there **performance improvements** that could be made?
- Is the **documentation** (installation instructions/vignettes/examples/demos) **clear and sufficient**?

Please be respectful and kind to the authors in your reviews. The rOpenSci [code of conduct](https://github.com/ropensci/onboarding/blob/master/policies.md/#code-of-conduct) is mandatory for everyone involved in our review process.

***

### session info


```{r sessionInfo}
sessionInfo()
```


```{r pkg_dir, echo = F}
pkg_dir <- "/private/var/folders/8p/87cqdx2s34vfvcgh04l6z72w0000gn/T/Rtmp4i9nQx/rdflib-review/../rdflib"
```

## Test installation

### test local `rdflib` install:

```{r test-local}
install(pkg_dir, dependencies = T, build_vignettes = T)
```

```{r github-rm}
remove.packages("rdflib")
```
#### **comments:**

<!-- record comments on local install here -->

***

### test install of `rdflib` from GitHub with:

```{r test-github}
devtools::install_github("cboettig/rdflib", dependencies = T, build_vignettes = T)
```

#### **comments:**

<!-- record comments on github install here -->

***



## Check package integrity

### run checks on `rdflib` source:

```{r check-checks}
devtools::check(pkg_dir)
```
#### **comments:**

<!-- record comments on checks here -->

***

### run tests on `rdflib` source:

```{r check-tests}
devtools::test(pkg_dir)
```
#### **comments:**

<!-- record comments on tests here -->

***


### check `rdflib` for goodpractice:

```{r test-goodpractice}
goodpractice::gp(pkg_dir)
```
#### **comments:**

<!-- record comments on goodpractice here -->

***

## Check package metadata files

### inspect

- #### [README](https://github.com/cboettig/rdflib)
- #### [DESCRIPTION](https://github.com/cboettig/rdflib/blob/master/DESCRIPTION)
- #### [NAMESPACE](https://github.com/cboettig/rdflib/blob/master/NAMESPACE)

### spell check

```{r spell-check}
devtools::spell_check(pkg_dir)
```

#### **comments:**

<!-- record comments on metadata files here -->

***

## Check documentation

online documentation: **<https://cboettig.github.io/rdflib/>**

* Is the documentation (installation instructions/vignettes/examples/demos) clear and sufficient?

### test `rdflib` function help files:

```{r test-help}
help(package = "rdflib")
```

#### **comments:**

<!-- record comments on help files here -->

***

### test `rdflib` vignettes:

```{r test-vignettes}
vignette(package = "rdflib")
```

#### **comments:**

<!-- record comments on vignettes here -->

***

## Test functionality:

- Are there **user interface improvements** that could be made?
- Are there **performance improvements** that could be made?

```{r free-style}
library("rdflib")
```

```{r parse-functions}
exports <-ls("package:rdflib")
exports
```

<!-- experiment with package functions -->

```{r exp-chunk}


```

#### **comments:**

<!-- record comments on rdflib experimentation here -->

***

## Inspect code:

- Does the package **comply with the [ROpenSci packaging guide](https://github.com/ropensci/onboarding/blob/master/packaging_guide.md)**?
    * good [function & variable naming?](https://github.com/ropensci/onboarding/blob/master/packaging_guide.md#funvar)
    * good [dependency management](https://github.com/ropensci/onboarding/blob/master/packaging_guide.md#deps)?
- Are there **improvements** that could be made to the **code style?**
- Is there **code duplication** in the package that should be reduced?

```{r inspect-code}
pkgreviewr::pkgreview_print_source("rdflib")
```
**\* might not be suitable for large packages with many exported functions**


<br>
<br>

#### **comments:**

<!-- record comments on rdflib source code here -->


## Review test suite:

### test coverage

```{r pkg_coverage}
covr::package_coverage(pkg_dir)

```

### inspect [tests](https://github.com/cboettig/rdflib/blob/master/tests/testthat)


#### **comments:**

<!-- record comments on testing suite here -->


***
